### 2016-04-27 config/glossaries.inc.tex
Lots of work on CH03
Uniform commands: part 1
Link to Stenman
Solve some warnings

\usepackage[sanitize={symbol=false},toc,acronym,section=section,nonumberlist,xindy]{glossaries}

@@

\renewcommand{\newacronym}[4][]{\newglossaryentry{#2}{type=\acronymtype,
name={#3},
description={#4},
text={#3},
first={#4~(#3)},
plural={#3\glspluralsuffix},
firstplural={#4\glspluralsuffix~(#3\glspluralsuffix)},
#1}}

@@

\newsymbolglos{matrix-eye}{\I_n}{ $n \times n$ identity matrix}

@@

\newsymbolglos{operator-cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
\newsymbolglos{operator-ln}{\ln}{Natural logarithm}
\newsymbolglos{operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
\newsymbolglos{operator-log}{\log_{B}}{Logarithm in base $B$ (when $B$ is omitted, $B=10$ is implied)}
\newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian (complex conjugated) transpose of the matrix \placeholder}
\newsymbolglos{operator-matrix-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
\newsymbolglos{operator-matrix-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
\newsymbolglos{operator-matrix-conv}{\conv}{Convolution}
\newsymbolglos{operator-matrix-kron}{\kron}{Kronecker product of matrices (\code{kron})}
\newsymbolglos{operator-matrix-hadamard}{\hadamard}{Hadamard (element-wise) product of matrices (\code{.*})}
\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer, as in \glsentrytext{IEEE} 754-2008 (\code{round})}

@@

\newacronym{LCF}{LCF}{left co-prime factorization}
\newacronym{LFT}{LFT}{linear fractional transformation}
\newacronym{LML}{LML}{log marginal likelihood}
\newacronym{LOOCV}{LOOCV}{leave-one-out cross-validation}
\newacronym{LMM}{LMM}{Local Modeling Method}
\newacronym{LPM}{LPM}{Local Polynomial Method}
\newacronym{LPV}{LPV}{linear parameter-varying}
\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
\newacronym{LRM}{LRM}{Local Rational Method}
\newacronym{LS}{LS}{least-squares}
\newacronym{LTI}{LTI}{linear time-invariant}
\newacronym{LTV}{LTV}{linear time-varying}

>>>>

\usepackage[toc,acronym,section=section,nonumberlist,xindy]{glossaries}

@@

\renewcommand{\newacronym}[4][]{\newglossaryentry{#2}{type=\acronymtype,
name={#3},
short={#3},
long={#4},
shortplural={#3\glspluralsuffix},
longplural={#4\glspluralsuffix},
description={#4},
text={#3},
first={#4~(#3)},
plural={#3\glspluralsuffix},
firstplural={#4\glspluralsuffix~(#3\glspluralsuffix)},
#1}}

@@

\newsymbolglos{matrix-eye-square}{\Identity{n}}{$n \times n$ identity matrix}
\newsymbolglos{matrix-eye}{\Identity{n \times m}}{$n \times m$ identity matrix}
\newsymbolglos{matrix-zero}{\Zero{n\times m}}{ $n \times m$ matrix containing only zeros}

@@

\newsymbolglos{operator-bias}{\bias{\placeholder}}{Bias of \placeholder}
\newsymbolglos{operator-cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
\newsymbolglos{operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
\newsymbolglos{operator-exp}{\E{\placeholder}}{Expected value of \placeholder}
\newsymbolglos{operator-ln}{\ln}{Natural logarithm}
\newsymbolglos{operator-log}{\log_{B}}{Logarithm in base $B$ (when $B$ is omitted, $B=10$ is implied)}
\newsymbolglos{operator-matrix-conv}{\conv}{Convolution}
\newsymbolglos{operator-matrix-hadamard}{\hadamard}{Hadamard (element-wise) product of matrices (\code{.*})}
\newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian (complex conjugated) transpose of the matrix \placeholder}
\newsymbolglos{operator-matrix-kron}{\kron}{Kronecker product of matrices (\code{kron})}
\newsymbolglos{operator-matrix-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
\newsymbolglos{operator-matrix-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer, as in \glsentrytext{IEEE} 754-2008 (\code{round})}
\newsymbolglos{operator-var}{\var{\placeholder}}{Variance of \placeholder}

@@

\newacronym{LCF}{LCF}{left co-prime factorization}
\newacronym{LFT}{LFT}{linear fractional transformation}
\newacronym{LML}{LML}{log marginal likelihood}
\newacronym{LOOCV}{LOOCV}{leave-one-out cross-validation}
\newacronym{LOWESS}{LOWESS}{locally weighted scatterplot smoothing}
\newacronym{LMM}{LMM}{Local Modeling Method}
\newacronym{LPM}{LPM}{Local Polynomial Method}
\newacronym{LPV}{LPV}{linear parameter-varying}
\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
\newacronym{LRM}{LRM}{Local Rational Method}
\newacronym{LS}{LS}{least-squares}
\newacronym{LTI}{LTI}{linear time-invariant}
\newacronym{LTV}{LTV}{linear time-varying}
